Alex's Notes and Text Fragments for the JSS Manuscript

### 2021-05-25 paper/paper.Rmd

@@

Since re-using the learning sample $\mathcal{L}$ for testing, i.e. $\mathcal{T}=\mathcal{L}$, would result in the over-optimistic *resubstitution* or *apparent* performance, cross-validation partitions the sample $\mathcal{L}$ into disjoint training and test sets.
Specifically, $\mathcal{L}$ is split into $k$ partitions,
\[
\mathcal{L} = \mathcal{L}_1 \cup \ldots \cup \mathcal{L}_k,\qquad \mathcal{L}_i\cap \mathcal{L}_j = \emptyset\quad \textrm{for all}\ i\neq j,
\]
and a model $\hat{f}_{(i)}$ is fitted on $\mathcal{L}_{(i)} := \mathcal{L}\setminus \mathcal{L}_i$, while $\mathcal{L}_i$ is withheld for testing.
This is repeated for $i=1,\ldots,k$ in order to effectively use the entire sample for testing, while keeping training and test sets disjoint at all times.
The $k$-fold CV estimator can therefore be written as
\[
\widehat{\mathit{perf}}_{\mathcal{L}, CV}(f) := \frac{1}{k}\sum_{i=1}^k\widehat{\mathit{perf}}_{\mathcal{L}_i}(\hat{f}_{\mathcal{L}_{(i)}}),
\]
where $f$ is a machine-learning algorithm, i.e. a mapping that trains a model $\hat{f}_\mathcal{S}$ using any suitable training sample $\mathcal{S}$.
The use of $k=5$ or $k=10$ folds is most commonly seen in practice, and these preferences are also supported by theory [ref??].
The $k$-fold CV estimator of model performance is a nearly unbiased estimator of the conditional performance measure when the observations were drawn independently [@efron1983].
Since $\widehat{\mathit{perf}}_{\mathcal{L}, CV}(f)$ still depends on the particular partitioning chosen for $L$, it is sometimes recommended to repeat the estimation using different random partitionings ($r$-repeated $k$-fold cross-validation, e.g. $k=100$; ref??).

@@

A variant of cross-validation is leave-one-out (LOO) cross-validation , which has long been established in geostatistics [@cressie1993], sometimes with a focus on the spatial distribution of LOO error [@willmott2006].
Since this is just a special case of non-spatial CV with $k=n$, it is sometimes also referred to as spatial CV [@willmott2006].
Nevertheless, spatial variants have been proposed that apply an exclusion buffer to the test locations to separate them from the training data [@brenning2005].
One plausible approach for this is to use the range of autocorrelation of model residuals to determine the buffer distance as this ensures independence conditional on the predictors [@brenning2005].
When data is grouped, e.g., due to multi-level sampling designs or the study of spatial objects, LOO at has been proposed at the site level [@martin2008; @kasurak2011] or, in animal movement studies, at the animal level [@anderson2005].
Similarly, in the temporal domain, it has been proposed to leave out temporal observational units, as in leave-one-year-out CV [@anderson2005; @brenning2005].

>>>>

Thus, \pkg{mlr3spatiotempcv} implements for the first time a comprehensive state-of-the-art compilation of spatial and spatiotemporal partitioning schemes that is well-integrated into a major machine learning framework in R, the \pkg{mlr3} ecosystem [@mlr3].
This package is furthermore equipped with a variety of two- and three-dimensional diagram types.
Our hope is that implementation will facilitate reproducible geospatial modelling and code-sharing across a broad range of application domains.

@@

Since re-using the learning sample $\mathcal{L}$ for testing, i.e. $\mathcal{T}=\mathcal{L}$, would result in the over-optimistic *resubstitution* or *apparent* performance, cross-validation partitions the sample $\mathcal{L}$ into disjoint training and test sets.
Specifically, $\mathcal{L}$ is split into $k$ partitions,
\[
\mathcal{L} = \mathcal{L}_1 \cup \ldots \cup \mathcal{L}_k,\qquad \mathcal{L}_i\cap \mathcal{L}_j = \emptyset\quad \textrm{for all}\ i\neq j,
\]
and a model $\hat{f}_{(i)}$ is fitted on $\mathcal{L}_{(i)} := \mathcal{L}\setminus \mathcal{L}_i$, while $\mathcal{L}_i$ is withheld for testing.
This is repeated for $i=1,\ldots,k$ in order to effectively use the entire sample for testing, while keeping training and test sets disjoint at all times.
The $k$-fold CV estimator can therefore be written as
\[
\widehat{\mathit{perf}}_{\mathcal{L}, CV}(f) := \frac{1}{k}\sum_{i=1}^k\widehat{\mathit{perf}}_{\mathcal{L}_i}(\hat{f}_{\mathcal{L}_{(i)}}),
\]
where $f$ is a machine-learning algorithm, i.e. a mapping that trains a model $\hat{f}_\mathcal{S}$ using any suitable training sample $\mathcal{S}$.
The use of $k=5$ or $k=10$ folds is most commonly seen in practice, and these preferences are also supported by theory [@bengio2004, @cawley2010].
The $k$-fold CV estimator of model performance is a nearly unbiased estimator of the conditional performance measure when the observations were drawn independently [@efron1983].
Since $\widehat{\mathit{perf}}_{\mathcal{L}, CV}(f)$ still depends on the particular partitioning chosen for $L$, it is sometimes recommended to repeat the estimation using different random partitionings ($r$-repeated $k$-fold cross-validation) to reduce the influence of randomness when creating partitions [@vanwinckelen2012].

@@

A variant of cross-validation is leave-one-out (LOO) cross-validation, which has long been established in geostatistics [@cressie1993], sometimes with a focus on the spatial distribution of LOO error [@willmott2006].
Since this is just a special case of non-spatial CV with $k=n$, it is sometimes also referred to as spatial CV [@willmott2006].
Nevertheless, spatial variants have been proposed that apply an exclusion buffer to the test locations to separate them from the training data [@brenning2005].
One plausible approach for this is to use the range of autocorrelation of model residuals to determine the buffer distance as this ensures independence conditional on the predictors [@brenning2005].
When data is grouped, e.g., due to multi-level sampling designs or the study of spatial objects, LOO at has been proposed at the site level [@martin2008; @kasurak2011] or, in animal movement studies, at the animal level [@anderson2005].
Similarly, in the temporal domain, it has been proposed to leave out temporal observational units, as in leave-one-year-out CV [@anderson2005; @brenning2005].
